\documentclass{brandeis-dissertation}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\cata}{\mathcal{A}}
\newcommand{\catc}{\mathcal{C}}
\newcommand{\catd}{\mathcal{D}}
\newcommand{\catt}{\mathcal{T}}
\newcommand{\cate}{\mathcal{E}}
\newcommand{\catf}{\mathcal{F}}
\newcommand{\cattf}{(\mathcal{T},\mathcal{F})}
\newcommand{\fz}{\tilde{\mathbb{Z}}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\sig}{\sigma}
\newcommand{\tsig}{\tilde{\sigma}}
\newcommand{\siginv}{{\sigma}^{-1}}
\newcommand{\psig}{P_{\sigma}}
\newcommand{\psiginv}{{P_{\sigma}}^{-1}}
\newcommand{\eem}[2]{\begin{bmatrix}#1\\#2\end{bmatrix}}
\newcommand{\abovearrow}[1]{\overset{#1}{\longrightarrow}}
\newcommand{\hos}{$Hom^{\leq 0}$-orthogonal sequence}
%Triangulated categories
\newcommand{\triang}[4]{#1\to #2\to #3\to #4}%triangle, math mode required
\newcommand{\tmtriang}[4]{$#1\to #2\to #3\to #4$}%triangle, text mode required
\newcommand{\triangwm}[7]{#1\overset{#2}{\to} #3\overset{#4}{\to} #5\overset{#6}{\to} #7}%triangle with morphisms, math mode required, some morphisms can be omitted
\newcommand{\tmtriangwm}[7]{$#1\overset{#2}{\to} #3\overset{#4}{\to} #5\overset{#6}{\to} #7$}%triangle with morphisms, text mode required, some morphisms can be omitted
\newcommand{\rightdoublearrow}{\arrow[r, shift right=0.6ex]\arrow[r, shift left=0.6ex]}
\newcommand{\leftquadruplearrow}{\arrow[l, shift right=1.2ex]\arrow[l, shift left=0.4ex]\arrow[l, shift right=0.4ex]\arrow[l, shift left=1.2ex]}
\newcommand{\righttwicedoublearrow}{\arrow[rr, shift right=0.6ex]\arrow[rr, shift left=0.6ex]}
\newcommand{\lefttwicedoublearrow}{\arrow[ll, shift right=0.6ex]\arrow[ll, shift left=0.6ex]}
\newcommand{\lefttwicetriplearrow}{\arrow[ll, shift right=0.8ex]\arrow[ll]\arrow[ll, shift left=0.8ex]}
%    Absolute value notation
\newcommand{\abs}[1]{\lvert#1\rvert}
% a_ig_j element
\newcommand{\ag}[2]{a_{#1}g_{#2}}

%    Blank box placeholder for figures (to avoid requiring any
%    particular graphics capabilities for printing this document).
\newcommand{\blankbox}[2]{%
  \parbox{\columnwidth}{\centering
%    Set fboxsep to 0 so that the actual size of the box will match the
%    given measurements more closely.
    \setlength{\fboxsep}{0pt}%
    \fbox{\raisebox{0pt}[#2]{\hspace{#1}}}%
  }%
}
%\numberwithin{equation}{section}
\title{Four problems related to maximal green sequences}
\author{Ying Zhou}
\department{Department of Mathematics}
\advisor{Kiyoshi Igusa, Department of Mathematics}
\reader{Olivier Bernardi, Department of Mathematics}
\reader{Gordana Todorov, Department of Mathematics, Northeastern University}
\dean{Eric Chasalow}
\graduationyear{2019}
\graduationmonth{May}
\acknowledgments{
\indent First of all I would like to thank my advisor, Kiyoshi Igusa for his constant patience, dedication and support. I also would like to thank Gordana Todorov for being my de facto second advisor. I would like to thank Otto Kerner, Hugh Thomas, Mike Prest and Nathan Reading for their guidance. I also would like to thank Alex Martsinkovsky, Ralf Schiffler, Thomas Br\"ustle, Dan Zacharia, Graham Leuschke, Shiping Liu and Nathan Reading for their hospitality during my visits.\\
\indent I would like to thank my wonderful colleagues who worked and work in the same field as me, such as Charles Paquette, Hipolito Treffinger, Dylan Rupel, Steve Hermes, Alexander Garver, Kaveh Mousavand, Jacob Matherne, Emily Barnard, Shijie Zhu, Van Nguyen, Job Rock, Eric Hanson, Matt Garcia, Moses Kim and PJ Apruzzese. I also would like to thank Jordan Tirrell, Devin Murray, Joshua Eike, Daoyuan Han, Shahriar Mirzadeh, Tarakaram Gollamudi, Aaron Berkowitz, Nick Wadleigh, Cristobal Lemus-Vidales, Qing Liu, Anurag Rao and Mishel Skenderi. My life at Brandeis would have been boring without you all.\\
\indent Special thanks go to Susan Parker, Becci Torrey and Keith Merrill for being such great course coordinators. I also would like to thank Alex Mitchell, Yuze He, Daniel Johnston, Prabu Gugagantha and many other undergrads I have taught, helped and chatted with for the great time we spent together.\\ %I also would like to thank Janet Ledda, Anthony Bottaro, Catherine Broderick and Emily Palmer for their help.\\
\indent Finally I would like to thank my family and other friends.}
\thesisabstract{Maximal green sequences were invented by Bernhard Keller and have a lot of applications in cluster algebra and particle physics. In this dissertation I will discuss four separate topics related to maximal green sequences. First of all I will discuss the problem of associated permutations of mutation sequences and establish a formula for the associated permutation in the case of $A_n$ straight orientation which answers a question raised at a workshop in Snowbird, Utah in 2014. Secondly I will introduce the concept of $m$-maximal green sequences and discuss the problem of $m$-maximal green sequence-finiteness of path algebras of tame quivers which generalizes a result by Br\"ustle, Dupont and Perotin. Then I will introduce two alternative definitions of $m$-maximal green sequences of hereditary algebras and show that they are both equivalent to the known ones which extends a result by Igusa. Finally I will discuss the problem of maximal green sequences in quivers with multiple edges and fully describe maximal green sequences of quivers with multiple edges which is the first step towards a proof of the conjecture that all acyclic quivers have finitely many maximal green sequences.}
\begin{document}
%\signaturepage*
\thesisfront
%\input{chapter_intro}
\input{chapter_background}
\input{chapter_permutation}
\input{chapter_tame}
\input{chapter_alternative_definitions}
\input{chapter_multiple_edges}
%\begin{}
\bibliographystyle{amsplain}
\begin{thebibliography}{10}
\bibitem{AI10} Takuma Aihara and Osamu Iyama, \textit{Silting mutation in triangulated categories}, J London Math Soc (2012) 85 (3): 633-668.
\bibitem{ARS} Maurice Auslander, Idun Reiten and Sverre O. Smalo, \textit{Representation Theory of Artin Algebras}, Cambridge University Press, Aug 21, 1997.
\bibitem{ASS06} Ibrahim Assem, Daniel Simson and Andrzej Skowronski, \textit{Elements of the Representation Theory of Associative Algebras, Volume 1, Techniques of Representation Theory}, London Mathematical Society Student Texts, 2006.
\bibitem{BBD} A.A. Beilinson, J. Bernstein, Pierre Deligne, \textit{Analyse et topologie sur les espaces singuliers}, Ast\'erisque 100, 1983. (in French)
\bibitem{B07} Tom Bridgeland, \textit{Stability Conditions on Triangulated Categories}, Annals of Mathematics, vol. 166, no. 2, 2007, pp. 317-345. JSTOR, \href{www.jstor.org/stable/20160065}{www.jstor.org/stable/20160065}.
\bibitem{BDP13} Thomas Br\"ustle, Gr\'{e}goire Dupont and Matthieu P\'{e}rotin, \textit{On Maximal Green Sequences},  Int Math Res Notices (2014), 4547-4586.
\bibitem{BHIT15} Thomas Br\"ustle, Stephen Hermes, Kiyoshi Igusa and Gordana Todorov, \textit{Semi-invariant pictures and two conjectures on maximal green sequences}, J Algebra {\bf 473} (2017): 80-109.
\bibitem{BST17} Thomas Br\"ustle, David Smith and Hipolito Treffinger, \textit{Stability conditions, $\tau$-tilting Theory and Maximal Green Sequences}, \href{https://arxiv.org/abs/1705.08227}{arXiv:1705.08227 [math.RT]}, 2017.
\bibitem{BST18A} Thomas Br\"ustle, David Smith and Hipolito Treffinger, \textit{Wall and Chamber Structure for finite-dimensional Algebras}\href{https://arxiv.org/abs/1805.01880}{arXiv:1805.01880 [math.RT]}, 2018.
\bibitem{BST18B} Thomas Br\"ustle, David Smith and Hipolito Treffinger, \textit{Stability Conditions and Maximal Green Sequences in Abelian Categories}, \href{https://arxiv.org/abs/1805.04382}{arXiv:1805.04382 [math.RT]}, 2018.
\bibitem{BY13} Thomas Br\"ustle and Dong Yang, \textit{Ordered Exchange Graphs}, Advances in Representation Theory of Algebras, 135--193, EMS Ser. Congr. Rep., Eur. Math. Soc., Zürich, 2013.
\bibitem{C15} Alfredo N\'{a}jera Ch\'{a}vez, \textit{On the $c$-Vectors of an Acyclic Cluster Algebra}, International Mathematics Research Notices, Volume 2015, Issue 6, 2015, Pages 1590?1600, \href{https://doi.org/10.1093/imrn/rnt264}.
\bibitem{DR76} Vlastimil Dlab and Claus Michael Ringel, \textit{Indecomposable representations of graphs and algebras}, Memoirs of AMS, Vol. 173, 1976.
\bibitem{DWZ08} Harm Derksen, Jerzy Weyman, Andrei Zelevinsky, \textit{Quivers with potentials and their representations I: Mutations}, A. Sel. math., New ser. (2008) 14: 59. \href{https://doi.org/10.1007/s00029-008-0057-9}.
\bibitem{DWZ10} Harm Derksen, Jerzy Weyman and Andrei Zelevinsky, \textit{Quivers with potentials and their representations II: Applications to cluster algebras}, J. Amer. Math. Soc. 23 (2010), 749-790 
\bibitem{EGNO} Pavel Etingof, Shlomo Gelaki, Dmitri Nikshych, Victor Ostrik, section 1.5 in \textit{Tensor categories}, Mathematical Surveys and Monographs, Volume 205, American Mathematical Society, 2015
\bibitem{FST11} Anna Felikson, Michael Shapiro, Pavel Tumarkin, \textit{Cluster algebras and triangulated orbifolds}, Advances in Mathematics, Volume 231, Issue 5, (2012) 2953-3002.
\bibitem{FZ01} Sergey Fomin and Andrei Zelevinsky, \textit{Cluster algebras I: Foundations}, J. Amer. Math. Soc. 15 (2002), 497-529.
\bibitem{FZ06} Sergey Fomin and Andrei Zelevinsky, \textit{Cluster algebras IV: Coefficients}, Compositio Math. 143 (2007) 112-164.
%\bibitem{Gab72} Peter Gabriel, \textit{Unzerlegbare Darstellungen. I}, Manuscripta Mathematica 6: 71ï¿½103, 1972. (in German)
\bibitem{GHKK14} Mark Gross, Paul Hacking, Sean Keel and Maxim Kontsevich, \textit{
Canonical bases for cluster algebras}, J. Amer. Math. Soc. 31 (2018), 497-608.
\bibitem{GM14} Alexander Garver and Gregg Musiker, \textit{On Maximal Green Sequences For Type $A$ Quivers}, G. J Algebr Comb (2017) 45: 553-599.
\bibitem{H88} Dieter Happel, \textit{Triangulated Categories in the Representation of Finite Dimensional Algebras}, London Mathematical Society Lecture Note Series, Cambridge: Cambridge University Press, 1988.
.%\bibitem{Igu14} Kiyoshi Igusa, \textit{Notes on picture groups and maximal green sequences}, 2014
\bibitem{IOTW15} Kiyoshi Igusa, Kent Orr, Gordana Todorov and Jerzy Weyman, \textit{Modulated semi-invariants},  \href{http://arxiv.org/abs/1507.03051}{arXiv:1507.03051 [math.RT]}.
\bibitem{IOTW4} Kiyoshi Igusa, Kent Orr, Gordana Todorov and Jerzy Weyman, \textit{Picture groups of finite type and cohomology in type $A_n$}, unpublished preprint, 2014.
%\bibitem{IT14} Kiyoshi Igusa and Gordana Todorov, \textit{Picture groups and maximal green sequences}, unpublished preprint 2014.
\bibitem{I17} Kiyoshi Igusa, \textit{Linearity of stability conditions}, \href{https://arxiv.org/abs/1706.06986}{arXiv:1706.06986}.
\bibitem{IT17} Kiyoshi Igusa and Gordana Todorov, \textit{Picture groups and maximal green sequences}, unpublished preprint 2014.
\bibitem{IY06} Osamu Iyama and Yuji Yoshino, \textit{Mutation in triangulated categories and rigid Cohen-Macaulay modules}, Y. Invent. math. (2008) 172: 117-168.
%\bibitem{IZ17} Kiyoshi Igusa and Ying Zhou, \textit{Tame Hereditary Algebras have finitely many m-Maximal Green Sequences}, \href{https://arxiv.org/abs/1706.09118}{arXiv:1706.09118}.
\bibitem{Kel11} Bernhard Keller, \textit{Quiver mutation and quantum dilogarithm identities}, Representations of Algebras and Related Topics, Editors A. Skowronski and K. Yamagata, EMS Series of Congress Reports, European Mathematical Society (2011): 85-116.
\bibitem{KQ15} Alastair King, Yu Qiu, \textit{Exchange graphs and Ext quivers}, Advances in Mathematics, Volume 285, 1106-1154, 2015.
\bibitem{KY12} Steffen Koenig and Dong Yang, \textit{Silting objects, simple-minded collections, t-structures and co-t-structures for finite-dimensional algebras}, Doc. Math. 19 (2014), 403-438. 
\bibitem{Mul15} Gregory Muller, \textit{The existence of a maximal green sequence is not invariant under quiver mutation}, Combinatorics, Volume 23, Issue 2 (2016) :P2.47. 
\bibitem{MurD1} Daniel Murfet, \href{http://therisingsea.org/notes/DerivedCategories.pdf}{Derived Categories Part I}.
\bibitem{MurD2} Daniel Murfet, \href{http://therisingsea.org/notes/DerivedCategoriesPart2.pdf}{Derived Categories Part II}.
\bibitem{MurT1} Daniel Murfet, \href{http://therisingsea.org/notes/TriangulatedCategories.pdf}{Triangulated Categories Part I}.
%\bibitem{NR15} Tomoki Nakanishi and Dylan Rupel, \textit{Companion cluster algebras to a generalized cluster algebra}, \href{http://arxiv.org/abs/1504.06758}{arXiv:1504.06758 [math.RA]}, 2015.
\bibitem{NZ11} Tomoki Nakanishi and Andrei Zelevinsky, \textit{On tropical dualities in cluster algebras}, Contemporary Mathematics 565, 217-226.
\bibitem{R84} Claus Michael Ringel, \textit{Tame Algebras and Integral Quadratic Forms}, Volume 1099 of \textit{Lecture Notes in Mathematics}, Springer-Verlag, 1984
\bibitem{S09} Sarah Scherotzke, \textit{Examples of Auslander-Reiten components in the bounded derived category}, \href{https://arxiv.org/abs/0906.4987}{arXiv:0906.4987 [math.RT]}, 2009.
\bibitem{Sal14} Ibrahim Saleh, \textit{Exchange Maps of Cluster Algebras}, \href{http://arxiv.org/abs/1011.0894v3}{arXiv:1011.0894 [math.RT]}, 2014.
\bibitem{SS06} Daniel Simson and Andrzej Skowronski, \textit{Elements of the Representation Theory of Associative Algebras, Volume 2, Tubes and Concealed Algebras of Euclidean Type}, London Mathematical Society Student Texts, 2006.
\bibitem{ST12} David Speyer, Hugh Thomas, \textit{Acyclic cluster algebras revisited}, In: Buan A., Reiten I., Solberg Ø. (eds) \textit{Algebras, Quivers and Representations. Abel Symposia}, vol 8. Springer, Berlin, Heidelberg.
\end{thebibliography}

\end{document}